Submission 1.1

### 2023-08-25 Submission 1.1.tex
Remove name + commentary Fixed wording in God problem

\title{Submission 1.1}
\author{Saffron Liu}
\date{}
\begin{document}
\maketitle

@@

                        $A \to B$\\
                        $B \to \neg A$\\
                        \rule{5em}{.5pt}\\
                        $\neg B$
                        \setcounter{enumii}{4}
                  \item  It is possible to be not right and also a fool.
            \end{enumerate}
      \item If I'm right, then I'm a fool. But if I'm a fool, I'm not right. Therefore, I'm not right. (B 70)
            \begin{enumerate}[(a)]
                  \item If I'm right, then I'm a fool.\\
                        If I'm a fool, then I'm not right.\\
                        \rule{15em}{.5pt}\\
                        I'm not right.
                  \item The argument is valid, but unsound because the premises may not be true.\\
                        \textit{Saffron's Commentary: I'm not sure whether or not the premises are contradictory? On one hand, if you're right you're a fool and if you're a fool you're not right doesn't seem to work, but it is possible to be a fool and not right without violating either premise. So it is possible for them to both be true at the same time, I think? Just very strange.\\
                              Update: An argument is always valid where the premises are inconsistent, because then there is never a counterexample.}
                  \item \textit{A}: I'm right\\
                        \textit{B}: I'm a fool\\

@@

                        $A \iff B$\\
                        $A \land \neg B$\\
                        \rule{5em}{.5pt}\\
                        $C$
                  \item \begin{tabular}{c|c|c|c|c}
                              A                      & B & C & $A \iff B$ & $A \land \neg B$ \\
                              \hline
                              \rowcolor{lightgray} T & T & T & T          & F                \\
                              \rowcolor{lightgray} T & T & F & T          & F                \\
                              \rowcolor{lightgray} T & F & T & F          & T                \\
                              \rowcolor{lightgray} T & F & F & F          & T                \\
                              \rowcolor{lightgray} F & T & T & F          & F                \\
                              \rowcolor{lightgray} F & T & F & F          & F                \\
                              \rowcolor{lightgray} F & F & T & T          & F                \\
                              \rowcolor{lightgray} F & F & F & T          & F                \\
                        \end{tabular}\\
                        There is no case where all premises are true, so the premises are contradictory and thus the argument is valid.
            \end{enumerate}
      \item God is omnipotent if and only if He can do everything. If He can't make a stone so heavy that He can't lift it, then he can't do everything. But if He can make a stone so heavy that He can't lift it, He can't do everything. Therefore, either God is not omnipotent or God does not exist. (B 132)
            \begin{enumerate}[(a)]
                  \item God is omnipotent if and only if he can do everything.\\
                        If he cannot make a stone so heavy that he cannot lift it, he cannot do everything.\\
                        If he can make a stone that he cannot lift, he cannot do everything.\\
                        \rule{15em}{.5pt}\\
                        Either god is not omnipotent or he does not exist.
                  \item The argument is valid. Soudness is difficult to determine.\\
                        \textit{Saffron's Commentary: I have no idea where the existence of God fits into that argument. In the English, it makes sense that it suddenly appears in the conclusion; in the logical notation, less so. I don't know whether that makes it invalid or not.\\
                              Update: I'm choosing to make his existence biconditional with his omnipotence.}
                  \item \textit{A}: God exists.\\
                        \textit{B}: God is omnipotent.\\
                        \textit{C}: God can do everything.\\
                        \textit{D}: God can make a stone which he cannot lift.\\

                        $A \leftrightarrow B$\\
                        $B \leftrightarrow C$\\
                        $\neg D \to \neg C$\\
                        $D \to \neg C$\\
                        \rule{5em}{.5pt}\\
                        $\neg B \lor \neg A$
                  \setcounter{enumii}{4}
                  \item Either God can or cannot make a stone so heavy that he cannot lift it. In either case, he cannot do anything and is thus not omnipotent. Thus, he is either not omnipotent, or does not exist, as his existence is biconditional with his omnipotence.
            \end{enumerate}
\end{enumerate}

@@

            \textit{Saffron's Commentary: I don't really know what contingent means! It's defined in the textbook, but I don't know if this question means “C is contingent upon $A \land B$” or simply “$(A \land B) \to C$” may be true or untrue depending on the case. I'm assuming the latter for this problem, but who knows.
                  Update: it's fine, probably? See theorem-argument exchange (Theorem 1.1).}\\

>>>>

\title{Submission 1.1}
% \author{Saffron Liu}
\date{}
\begin{document}
\maketitle

@@

                        $A \to B$\\
                        $B \to \neg A$\\
                        \rule{5em}{.5pt}\\
                        $\neg B$
                        \setcounter{enumii}{4}
                  \item  It is possible to be not right and also a fool.
            \end{enumerate}
      \item If I'm right, then I'm a fool. But if I'm a fool, I'm not right. Therefore, I'm not right. (B 70)
            \begin{enumerate}[(a)]
                  \item If I'm right, then I'm a fool.\\
                        If I'm a fool, then I'm not right.\\
                        \rule{15em}{.5pt}\\
                        I'm not right.
                  \item The argument is valid, but unsound because the premises may not be true.\\
                        % \textit{Saffron's Commentary: I'm not sure whether or not the premises are contradictory? On one hand, if you're right you're a fool and if you're a fool you're not right doesn't seem to work, but it is possible to be a fool and not right without violating either premise. So it is possible for them to both be true at the same time, I think? Just very strange.\\
                        %       Update: An argument is always valid where the premises are inconsistent, because then there is never a counterexample.}
                  \item \textit{A}: I'm right\\
                        \textit{B}: I'm a fool\\

@@

                        $A \iff B$\\
                        $A \land \neg B$\\
                        \rule{5em}{.5pt}\\
                        $C$
                  \item \begin{tabular}{c|c|c|c|c}
                              A                      & B & C & $A \iff B$ & $A \land \neg B$ \\
                              \hline
                              \rowcolor{lightgray} T & T & T & T          & F                \\
                              \rowcolor{lightgray} T & T & F & T          & F                \\
                              \rowcolor{lightgray} T & F & T & F          & T                \\
                              \rowcolor{lightgray} T & F & F & F          & T                \\
                              \rowcolor{lightgray} F & T & T & F          & F                \\
                              \rowcolor{lightgray} F & T & F & F          & F                \\
                              \rowcolor{lightgray} F & F & T & T          & F                \\
                              \rowcolor{lightgray} F & F & F & T          & F                \\
                        \end{tabular}\\
                        There is no case where all premises are true, so the premises are contradictory and thus the argument is valid.
            \end{enumerate}
      \item God is omnipotent if and only if He can do everything. If He can't make a stone so heavy that He can't lift it, then he can't do everything. But if He can make a stone so heavy that He can't lift it, He can't do everything. Therefore, either God is not omnipotent or God does not exist. (B 132)
            \begin{enumerate}[(a)]
                  \item God is omnipotent if and only if he can do everything.\\
                        If he cannot make a stone so heavy that he cannot lift it, he cannot do everything.\\
                        If he can make a stone that he cannot lift, he cannot do everything.\\
                        \rule{15em}{.5pt}\\
                        Either god is not omnipotent or he does not exist.
                  \item The argument is valid. Soudness is difficult to determine.\\
                        % \textit{Saffron's Commentary: I have no idea where the existence of God fits into that argument. In the English, it makes sense that it suddenly appears in the conclusion; in the logical notation, less so. I don't know whether that makes it invalid or not.\\
                        %       Update: I'm choosing to make his existence biconditional with his omnipotence.}
                  \item \textit{A}: God exists.\\
                        \textit{B}: God is omnipotent.\\
                        \textit{C}: God can do everything.\\
                        \textit{D}: God can make a stone which he cannot lift.\\

                        $A \leftrightarrow B$\\
                        $B \leftrightarrow C$\\
                        $\neg D \to \neg C$\\
                        $D \to \neg C$\\
                        \rule{5em}{.5pt}\\
                        $\neg B \lor \neg A$
                  \setcounter{enumii}{4}
                  \item Either God can or cannot make a stone so heavy that he cannot lift it. In either case, he cannot do everything and is thus not omnipotent. Thus, he is either not omnipotent, or does not exist, as his existence is biconditional with his omnipotence.
            \end{enumerate}
\end{enumerate}

@@

            % \textit{Saffron's Commentary: I don't really know what contingent means! It's defined in the textbook, but I don't know if this question means “C is contingent upon $A \land B$” or simply “$(A \land B) \to C$” may be true or untrue depending on the case. I'm assuming the latter for this problem, but who knows.
            %       Update: it's fine, probably? See theorem-argument exchange (Theorem 1.1).}\\
